### 2017-09-06 Graduate - Introduction to Analysis I/Assignment 2/2_Homework20170831.tex

\textbf{Necessity:} We first show that $\forall \epsilon > 0$, we can find an open set $O\supset E$, s.t. $m^*(O\setminus E) < \epsilon$. \\[2pt]
First, if $m^*(E) <\infty$. Then according to definition of outer measure, $\forall\epsilon > 0$, there is an open cover $\{O_i\}$ of $E$, s.t. 
$$
\sum_{i}m^*(O_i) < m^*(E)+\epsilon.
$$
Let $O = \bigcup_{i}O_i$, then $m^*(O) < m^*(E)+\epsilon$, and $O$ is an open set. Thus 
$$
m^*(O\setminus E) = m^*(E)-m^*(E\cap O) = m^*(O)-m^*(E) < \epsilon.
$$
If $m^*(E) = \infty$, define $E_{n} = \{x\in E:|x|\le n\}$. Then $E_n$ is measurable with finite outer measure, the argument above shows that there is an open set $O_k\supset E_k$, s.t.
$$
m^*(O_k\setminus E_k) < \frac{\epsilon}{2^k}.
$$
Then $O = \bigcup_{k} O_k$ is an open set that contains $E$, and 
$$
m^*(O\setminus E) = m^*\left(\bigcup_{k}O_k\setminus E\right)\le\sum_{k}m^*(O_k\setminus E)\le\sum_{k}m^*(O_k\setminus E_k)<\epsilon.
$$
So there is an open set $O\supset E$, s.t. $m^*(O\setminus E) < \frac{\epsilon}{2}$. Meanwhile, since $E^c$ is measurable, there is an open set $G\supset E^c$, s.t. $m^*(G\setminus E^c)<\frac{\epsilon}{2}$. Thus we have a closed set $F = G^c$, and $O\supset E\supset F$,
$$
m^*(O\setminus F) \le m^*(O\setminus E)+m^*(E\setminus F) = m^*(O\setminus E)+m^*(G\setminus E^c) < \epsilon.
$$
\\[2pt]
\textbf{(b):}
From (a) we know that $\forall \epsilon > 0$, there exists an open set $G$ and a closed set $F$, s.t. $G\supset E\supset F$. So 
$$
m(G\setminus E) \le m(G\setminus F) < \epsilon, ~m(E\setminus F) \le m(G\setminus F) < \epsilon.
$$
Thus we can construct two series of sets $\{G_k\}$ and $\{F_k\}$:
$$
G_k\supset E\supset F_k, ~m(G_k\setminus E) < \frac{\epsilon}{2^k}, ~m(E\setminus F_k) < \frac{\epsilon}{2^k}.
$$
Thus $G = \bigcap G_k$ is a $G_\delta$ set, and $F = \bigcup F_k$ is a $F_\sigma$ set, and
$$
m(G) - m^*(E) \le m(G\setminus E) < \frac{\epsilon}{2^n}, ~m^*(E)-m(F)\le m(E\setminus F) < \frac{\epsilon}{2^n}.
$$
Let $n\to\infty$, we have $m^*(E) = m(G) = m(F)$. \\[2pt]
\textbf{(c):}

\end{proof}
\bigskip

>>>>

\textbf{Necessity:} We first show that $\forall \epsilon > 0$, we can find an open set $O\supset E$, s.t. $m^*(O\setminus E) < \epsilon$. \\[2pt]
First, if $m^*(E) <\infty$. Then according to definition of outer measure, $\forall\epsilon > 0$, there is an open cover $\{O_i\}$ of $E$, s.t. 
$$
\sum_{i}m^*(O_i) < m^*(E)+\epsilon.
$$
Let $O = \bigcup_{i}O_i$, then $m^*(O) < m^*(E)+\epsilon$, and $O$ is an open set. Thus 
$$
m^*(O\setminus E) = m^*(E)-m^*(E\cap O) = m^*(O)-m^*(E) < \epsilon.
$$
If $m^*(E) = \infty$, define $E_{n} = \{x\in E:|x|\le n\}$. Then $E_n$ is measurable with finite outer measure, the argument above shows that there is an open set $O_k\supset E_k$, s.t.
$$
m^*(O_k\setminus E_k) < \frac{\epsilon}{2^k}.
$$
Then $O = \bigcup_{k} O_k$ is an open set that contains $E$, and 
$$
m^*(O\setminus E) = m^*\left(\bigcup_{k}O_k\setminus E\right)\le\sum_{k}m^*(O_k\setminus E)\le\sum_{k}m^*(O_k\setminus E_k)<\epsilon.
$$
So there is an open set $O\supset E$, s.t. $m^*(O\setminus E) < \frac{\epsilon}{2}$. Meanwhile, since $E^c$ is measurable, there is an open set $G\supset E^c$, s.t. $m^*(G\setminus E^c)<\frac{\epsilon}{2}$. Thus we have a closed set $F = G^c$, and $O\supset E\supset F$,
$$
m^*(O\setminus F) \le m^*(O\setminus E)+m^*(E\setminus F) = m^*(O\setminus E)+m^*(G\setminus E^c) < \epsilon.
$$
\\[2pt]
\textbf{(b):}
From (a) we know that $\forall \epsilon > 0$, there exists an open set $G$ and a closed set $F$, s.t. $G\supset E\supset F$. So 
$$
m(G\setminus E) \le m(G\setminus F) < \epsilon, ~m(E\setminus F) \le m(G\setminus F) < \epsilon.
$$
Thus we can construct two series of sets $\{G_k\}$ and $\{F_k\}$:
$$
G_k\supset E\supset F_k, ~m(G_k\setminus E) < \frac{\epsilon}{2^k}, ~m(E\setminus F_k) < \frac{\epsilon}{2^k}.
$$
Thus $G = \bigcap G_k$ is a $G_\delta$ set, and $F = \bigcup F_k$ is a $F_\sigma$ set, and
$$
m(G) - m^*(E) \le m(G\setminus E) < \frac{\epsilon}{2^n}, ~m^*(E)-m(F)\le m(E\setminus F) < \frac{\epsilon}{2^n}.
$$
Let $n\to\infty$, we have $m^*(E) = m(G) = m(F)$.

On the other hand, suppose there exists a $F_\sigma$ set $F$ contained in $E$, s.t. $m(F) = m^*(E)$. Then similar to the process of (a), $\forall \epsilon > 0$, there is an open set $G\supset E$, s.t. $m^*(G\setminus E) < \epsilon$. Thus $m^*(G\setminus F) < m^*(G\setminus E) + m^*(E\setminus F) < \epsilon$. Then $E$ is a measurable set.

\textbf{(c):}
Fisrt there exist an open set $O\supset E$ which has finite outer measure.
Suppose for each open set $O$ containing $E$ that has finite outer measure, 
$$
m^*(O\setminus E) \le m^*(O)-m^*(E).
$$
Then we have
$$
m^*(O\setminus E) = m^*(O)-m^*(E)
$$
according to the properties of outer measures. 
So according to the definition of outer measures, $\forall \epsilon > 0$, there is an open set $O\supset E$, s.t. $m^*(O)-m^*(E) < \epsilon$. This leads to $m^*(O\setminus E) < epsilon$. Accoding to Theorem 11 on Page 40, $E$ is measurable, which makes an contradiction. 
% Denote $\{O_k\}$ to be the set of open sets containing $E$, then $O = \bigcap O_k$ is the smallest $G_\sigma$ set containing $E$, but 
\end{proof}
\bigskip
